### 2013-06-14 Tex/chapters/monte_carlo.tex
kleinere Korrekturen an autocorr Section

\subsection{Equilibration- and Autocorrelation Time}
    To generate an equilibrium state one starts with an arbitrary state
    and waits until it is equilibrated. The count of sweeps till
    equilibrium is called \emph{equilibration time} \(t_{eq}\).
    All measurement should start after this time.
    % in meinem fall ... vielleicht bild?
    \\
    Because every state is generated from the state before, measurements
    of subsequent states are correlated. To determine when two states
    are independet, one calculates the autocorrelation function \(\chi(t)\)
    and integrates it to get the autocorrelation time \(\tau = \int \chi(t) \de t\).
    \(\tau\) is an estimate after which time two samples are not
    correlated anymore. \cite[S. ??]{NewmanBarkema1999} \cite[S. 150f]{Katzgraber2011}.
    To make sure that the error is not underestimated one should wait
    \(2\tau\) sweeps between two measurements.

>>>>

\subsection{Equilibration- and Autocorrelation Time}
    To generate an equilibrium state one starts with an arbitrary state
    and waits until it is equilibrated. The count of sweeps till
    equilibrium is called \emph{equilibration time} \(t_{eq}\).
    All measurement should start after this time.\\
    To determine when the system is in equilibrium, one can watch the
    development of some observables and take the point at which there
    are no big changes anymore as equilibrium. In fig.
    \ref{fig:equiandauto}\subref{sfig:equiandauto:equiE}
    the equilibrium is reached after approximately \(N=50\) sweeps for
    either a initial condition of all spins up and all spins random. It
    does not harm to double that value to be save.
    \begin{figure}[htbp]
        \centering
        \subfigure[Example of an equilibrating Ising system][]{
                \label{sfig:equiandauto:equiE}
                \includegraphics[width=0.45\textwidth]{plots/equiE}
        }
        \subfigure[Example of the autocorrelation of an Ising system][]{
                \label{sfig:equiandauto:autoM}
                \includegraphics[width=0.45\textwidth]{plots/autoM}
        }
        \caption[Examples for equilibration and autocorrelation]
                {\subref{sfig:equiandauto:equiE} Example of a Ising
                    system reaching equilibrium at \(T=2.36\) and
                 \subref{sfig:equiandauto:autoM} the
                    autocorrelation of an Ising system at \(T=2.40\)
                    (only Metropolis sweeps).
                }
        \label{fig:equiandauto}
    \end{figure}

    Because every state is generated from the state before, measurements
    of subsequent states are correlated. To determine when two states
    are independet, one calculates the normalized autocorrelation function
    \(\frac{\chi(t)}{\chi(0)}\) like in fig. \ref{fig:equiandauto}\subref{sfig:equiandauto:autoM}
    and integrates it to get the autocorrelation time \(\tau = \int \frac{\chi(t)}{\chi(0)} \de t\).
    \(\tau\) is an estimate after which time two samples are not
    correlated anymore. \cite[S. ??]{NewmanBarkema1999} \cite[S. 150f]{Katzgraber2011}.
    To make sure that the error is not underestimated one should wait
    \(2\tau\) sweeps between two measurements.
